---
title: "Project Feature Importance"
author: "Ofir Mizrahi"
date: "2018 M05 24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F)
library(sqldf)
library(ggplot2)
library(reshape2)
```

#######################################
understanding the top features by bic
#######################################


##Load Data

We are loading only projects with thier first project. Also, "personal" attribute is set as binary as results were better with it (instead of it being ordinal).

```{r}
path <- "C:\\Users\\Ofir\\Desktop\\Thesis\\Kickstarter\\sandboxCleaned.csv"
temp <- read.csv(path, header = T)
temp$X <- NULL

project <- temp[,c(6,24, 27,28,29,31,44,50,55,25)]
project <- project[!c(project$averageBackersRequired==Inf),]
rm(path,temp)
```


##Feature Importance for BIC
###Backward Step

Let's create a model with all features and then remove one of them and see how it affects the BIC measure.

We are using BIC meausure as there is not need to optimaize any parameter (such as threshold) as well as taking into conciderations the number of variables in the model.

The calculation done is part model BIC minus full model BIC. As we want to minimize BIC if we get:
a positive result, means adding the excluded feature to create the full model was creating a better model.
a negative result, means adding the excluded feature to create the full model was not needed and created a worst model.

The commentary on the plot is pretty stright forward.

The number of perks and average backers requiered are the only features still staying important.

On the statistical test side, we note that valuta is bad yet regarding Dev the full model is significantly better. Why so? because just like "continent" in the user set, this feature is categorical and creates many dummy variables (many levels) and so is penalized much more in the BIC.

```{r Backward Step}

features <- names(project)[1:ncol(project)-1]

string <- "success ~"
for (j in 1:length(features)) {
  if(j==1){
    string <- paste(string,features[j])
  }else{
    string <- paste(string,"+",features[j])
  }
}

lmFull  <- glm(formula= string, family = binomial(), data = project)


#bic
fullBIC <- AIC(lmFull, k=log(nrow(project)))

bic <- vector()
statDev <- vector()
statChi <- vector()

for (i in 1:length(features)) {
  current <- features[-i]
  string <- "success ~"
  for (j in 1:length(current)) {
    if(j==1){
      string <- paste(string,current[j])
    }else{
      string <- paste(string,"+",current[j])
    }
  }
  lmPart  <- glm(string, family = binomial(), data = project)
  partBIC <- AIC(lmPart, k=log(nrow(project)))
  bic[i] <- partBIC- fullBIC
  
  #create log ratio test
  LRT <- anova(lmFull,lmPart,test="Chi")
  #take the value for the residual deviance and p-val ([1] is for null dev)
  statDev[i] <- LRT$Deviance[2]
  statChi[i] <- LRT$`Pr(>Chi)`[2]
}

#create table for plot
res <- as.data.frame(cbind(features,bic,statDev,statChi,pvalColor=(statChi<0.05)))
res$bic <- as.numeric(as.character(res$bic))
res$statDev <- as.numeric(as.character(res$statDev))*(-1)
res$statChi <- round(as.numeric(as.character(res$statChi)),3)

#create the plot
ggplot(res)+
  geom_bar(aes(x=reorder(features, -bic), y=bic), stat = "identity")+
  xlab("Excluded Feature (from full model)")+
  ylab("BIC Difference (part-full)")+
  ggtitle("First Step Backwards (BIC)")+
  geom_label(aes(x=reorder(features, -bic), y=(min(bic)-1), label=statChi, fill= pvalColor),size=5)+
  theme(legend.position="none",axis.text.x = element_text(angle = 45, hjust = 1))

res <- melt(res)
#emphasis the relationship between deviance and BIC. We can see the same gap for each variable except "continent" (there also a bit different with "noFBfriends which it logic")
ggplot(res[!res$variable=="statChi",])+
  geom_bar(aes(x=features, y=value, fill=variable), stat = "identity",position = "dodge")

rm(bic,res,fullBIC,lmFull,features,current,string,i,j,lmPart,partBIC,LRT,statChi,statDev)

```


###Forward Step

Let's now create a model with no features (intercept only) and then add only one of the features and see how it affects the BIC measure.

The calculation done is empty model BIC minus part model BIC. As we want to minimize BIC if we get:
a positive result, means adding the excluded feature to create the full model was creating a better model.
a negative result, means adding the excluded feature to create the full model was not needed and created a worst model.

Steps forward is always somwhat more revealing. Here we can see that average money reward has information that is included in other features in the model. number of perks and average backers required still play an important role. Goal and duration do not influence as much as reaserch thinks.
Average money reward= (goal)/(number of perk levels) and Average backers required=(goal)/(mean of all perk $) therefore the top four most important features are all connected.

```{r Forward step}
lmEmpty <- glm(success ~ 1, family = binomial(), data = project)
emptyBIC <- AIC(lmEmpty, k=log(nrow(project)))


features <- names(project)[1:ncol(project)-1]
bic <- vector()
statDev <- vector()
statChi <- vector()

for (i in 1:length(features)) {
  current <- features[i]
  string <- paste("success ~",current)
  lmPart  <- glm(string, family = binomial(), data = project)
  partBIC <- AIC(lmPart, k=log(nrow(project)))
  bic[i] <- emptyBIC - partBIC 
  
  #create log ratio test
  LRT <- anova(lmPart,lmEmpty,test="Chi")
  #take the value for the residual deviance and p-val ([1] is for null dev)
  statDev[i] <- LRT$Deviance[2]
  statChi[i] <- LRT$`Pr(>Chi)`[2]
}

#create table for plot
res <- as.data.frame(cbind(features,bic,statDev,statChi,pvalColor=(statChi<0.05)))
res$bic <- as.numeric(as.character(res$bic))
res$statDev <- as.numeric(as.character(res$statDev))*(-1)
res$statChi <- round(as.numeric(as.character(res$statChi)),3)

#create the plot
ggplot(res)+
  geom_bar(aes(x=reorder(features, -bic), y=bic), stat = "identity")+
  xlab("Added Feature (to intercept)")+
  ylab("BIC Difference (empty-part)")+
  ggtitle("First Step Forward (BIC)")+
  geom_label(aes(x=reorder(features, -bic), y=(min(bic)-1), label=statChi, fill= pvalColor),size=5)+
  theme(legend.position="none",axis.text.x = element_text(angle = 45, hjust = 1))

rm(bic,res,emptyBIC,lmEmpty,features,current,string,i,lmPart,partBIC,LRT,statChi,statDev)
```
