---
title: "Sections Analysis"
author: "Ofir Mizrahi"
date: "2018 M05 31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(corrplot)
library(ggcorrplot)
library(sqldf)
library(plotly)
library(rcompanion)
```


#####################################################
understanding the top features by bic and aic
#####################################################

##Load Tables

We will load the 3 tables (mostly for thier feature names). We will use the rows from perk table as we only took away the INF values, we still want to predict success for users where this is not thier first project.
For each table, We took down features that in the feature analysis donated nothing.
```{r}
#project table
path <- "C:\\Users\\Ofir\\Desktop\\Thesis\\Kickstarter\\projectBinaryWeb.csv"
project <- read.csv(path, header = T)
project$X <- NULL

project <- project[,c(4:10,17)]
rm(path)

#user table
path <- "C:\\Users\\Ofir\\Desktop\\Thesis\\Kickstarter\\userBinaryWeb.csv"
user <- read.csv(path, header = T)
user$X <- NULL
user$continent <- NULL
user$noFacebookFriends <- NULL

rm(path)

#perk table
path <- "C:\\Users\\Ofir\\Desktop\\Thesis\\Kickstarter\\sandboxCleaned.csv"
temp <- read.csv(path, header = T)
temp$X <- NULL

#with valuta and highestPerk or without
perk <- temp[,c(6,24, 27,28,29,31,44,50,55,25)]
#perk <- temp[,c(6,27,29,31,44,50,55,25)]
perk <- perk[!c(perk$averageBackersRequired==Inf),]
rm(path,temp)


#create total table
path <- "C:\\Users\\Ofir\\Desktop\\Thesis\\Kickstarter\\sandboxCleaned.csv"
data <- read.csv(path, header = T)
data$X <- NULL
data <- data[!c(data$averageBackersRequired==Inf),]

#add personal attribute to total table
path <- "C:\\Users\\Ofir\\Desktop\\Thesis\\Kickstarter\\personalSite.csv"
temp <- read.csv(path, header = T)
temp$X <- NULL


data <- sqldf("select *
from data left join temp on temp.url=data.url")

data$url <- NULL
data$url <- NULL

#remove success to the end of table
temp <- data$success
data$success <- NULL
data$success <- temp

#select only relevant feature
features <- c(names(perk)[1:ncol(perk)-1],names(project)[1:ncol(project)-1],names(user)[1:ncol(user)])
userFeatures <- names(user)[1:ncol(user)-1]
perkFeatures <- names(perk)[1:ncol(perk)-1]
projectFeatures <- names(project)[1:ncol(project)-1]

data[is.na(data$personal),"personal"] <- 0
#screen data for only first projects or not
data <- data[(data$created!=1),]
data <- data[,c(features)]


rm(user,perk,project, path, temp)
```


#Step Backward (BIC & AIC & nagelkerke)

Create the steps excluding the entire set each time.
Because we don't want to penalize for number of features we use AIC as well but we can see results are the same.

As we are comparing whole sets, creating a pie chart is wrong at the sum of all parts does not represent a whole.
Also, comparing by bic or deviance is problematic as we are now comparing sets of features.
We shall make use of the nagelkerke pseudo $R^2$. As the concept of residuals can not easily be defined in GLM models and the likelihood is used instead we want to generalize the measure by using the likelihood.
The first form proposed by Cox&Snell:
$$R^2=1-exp^{-(2/n)*(l(\beta)-l(0))}=1-[L(0)/L(\beta)]^{2/n}$$
where $l(0)$ and $l(\beta)$ denote the log likelihoods of the null and the fitted
model respectively.

Nagelkerke showed that the current $R^2$ suggested does not reach the maximum of 1 like it should. This happens in discrete models such as the logistic regression, where the likelihood is a product of probabilities with mazimum of 1.
The maximun $R^2$ for a model is:
$max(R^2)=1-L(0)^{2/n}$
Therefore to understand what percent we managed to explained should be taken into proportion with the maximum possible explanation for our model.
Hence we will divide the $R^2$ we get by the $max(R^2)$

```{r}
string <- "success ~"
for (j in 1:length(features)) {
  if(j==1){
    string <- paste(string,features[j])
  }else{
    string <- paste(string,"+",features[j])
  }
}

lmFull  <- glm(formula= string , family = binomial(), data = data)

#bic
fullBIC <- AIC(lmFull, k=log(nrow(data)))
fullAIC <- AIC(lmFull, k=2)

nag <- nagelkerke(lmFull)
nagFull <- nag$Pseudo.R.squared.for.model.vs.null[3]

bic <- vector()
aic <- vector()
statDev <- vector()
statChi <- vector()
nagPart <- vector()

#########################No perks
current <- c(userFeatures,projectFeatures)
string <- "success ~"
for (j in 1:length(current)) {
  if(j==1){
    string <- paste(string,current[j])
  }else{
    string <- paste(string,"+",current[j])
  }
}
lmPart  <- glm(string, family = binomial(), data = data)

partBIC <- AIC(lmPart, k=log(nrow(data)))
partAIC <- AIC(lmPart, k=2)
bic[1] <- partBIC- fullBIC
aic[1] <- partAIC- fullAIC

#create log ratio test
LRT <- anova(lmFull,lmPart,test="Chi")
#take the value for the residual deviance and p-val ([1] is for null dev)
statDev[1] <- LRT$Deviance[2]
statChi[1] <- LRT$`Pr(>Chi)`[2]

nag <- nagelkerke(lmPart)
nagPart[1] <- nag$Pseudo.R.squared.for.model.vs.null[3]

#######################No user
current <- c(perkFeatures,projectFeatures)
string <- "success ~"
for (j in 1:length(current)) {
  if(j==1){
    string <- paste(string,current[j])
  }else{
    string <- paste(string,"+",current[j])
  }
}
lmPart  <- glm(string, family = binomial(), data = data)
partBIC <- AIC(lmPart, k=log(nrow(data)))
partAIC <- AIC(lmPart, k=2)
bic[2] <- partBIC- fullBIC
aic[2] <- partAIC- fullAIC

#create log ratio test
LRT <- anova(lmFull,lmPart,test="Chi")

#take the value for the residual deviance and p-val ([1] is for null dev)
statDev[2] <- LRT$Deviance[2]
statChi[2] <- LRT$`Pr(>Chi)`[2]

nag <- nagelkerke(lmPart)
nagPart[2] <- nag$Pseudo.R.squared.for.model.vs.null[3]

########################No project
current <- c(userFeatures,perkFeatures)
string <- "success ~"
for (j in 1:length(current)) {
  if(j==1){
    string <- paste(string,current[j])
  }else{
    string <- paste(string,"+",current[j])
  }
}
lmPart  <- glm(string, family = binomial(), data = data)
partBIC <- AIC(lmPart, k=log(nrow(data)))
partAIC <- AIC(lmPart, k=2)
bic[3] <- partBIC- fullBIC
aic[3] <- partAIC- fullAIC

#create log ratio test
LRT <- anova(lmFull,lmPart,test="Chi")

#take the value for the residual deviance and p-val ([1] is for null dev)
statDev[3] <- LRT$Deviance[2]
statChi[3] <- LRT$`Pr(>Chi)`[2]

nag <- nagelkerke(lmPart)
nagPart[3] <- nag$Pseudo.R.squared.for.model.vs.null[3]

#calculate the gap in explanation when the set is removed
print(1-(nagPart/nagFull))

#create table for plot
lables <- c("finance","entrepreneur", "pitch")

res <- as.data.frame(cbind(lables,bic,statDev,statChi,pvalColor=(statChi<0.05)))
res$bic <- as.numeric(as.character(res$bic))
res$statDev <- as.numeric(as.character(res$statDev))*(-1)
res$statChi <- round(as.numeric(as.character(res$statChi)),3)


#create the deviance plot
ggplot(res)+
  geom_bar(aes(x=reorder(lables, -statDev), y=statDev), stat = "identity")+
  xlab("Excluded Feature (from full model)")+
  ylab("BIC Difference (part-full)")+
  ggtitle("First Step Backwards (BIC)")+
  geom_label(aes(x=reorder(lables, -statDev), y=0, label=statChi, fill= pvalColor),size=5)+
  xlab("Excluded Feature (from full model)")+ylab("Deviance Difference (part-full)")+ggtitle("Step Backwards (BIC)")+ theme(legend.position="none",axis.text.x = element_text(angle = 45, hjust = 1))+scale_fill_manual(values = c("white"))


#AIC plot
res2 <- as.data.frame(cbind(lables,aic))
res2$aic <- as.numeric(as.character(res2$aic))
ggplot(res2)+geom_bar(aes(x=reorder(lables, -aic), y=aic, fill="blue"), stat = "identity")+xlab("Excluded Features (from full model)")+ylab("AIC Difference (part-full)")+ggtitle("Step Backwards (AIC)")+ theme(text = element_text(size=20))+scale_fill_manual(values = c("#3690c0"))

rm(bic,res,res2,fullBIC,lmFull,current,string,i,j,lmPart,partBIC, aic, fullAIC, lables, partAIC,LRT,statChi,statDev, nagPart, nag)
```

#Step Forward (BIC & AIC)

Create the steps including the entire set each time.
Because we don't want to penalize for number of features we use AIC as well but we can see results are the same.
Create pie charts as well to emphasize the difference between sets.

```{r}
lmEmpty <- glm(success ~ 1, family = binomial(), data = data)
emptyBIC <- AIC(lmEmpty, k=log(nrow(data)))
emptyAIC <- AIC(lmEmpty, k=2)


features <- names(data)[1:ncol(data)-1]
bic <- vector()
aic <- vector()
statDev <- vector()
statChi <- vector()
nagPart <- vector()

##################only user
current <- userFeatures
string <- "success ~"
for (j in 1:length(current)) {
  if(j==1){
    string <- paste(string,current[j])
  }else{
    string <- paste(string,"+",current[j])
  }
}
lmPart  <- glm(string, family = binomial(), data = data)
partBIC <- AIC(lmPart, k=log(nrow(data)))
partAIC <- AIC(lmPart, k=2)
bic[1] <- emptyBIC - partBIC
aic[1] <- emptyAIC - partAIC

#create log ratio test
LRT <- anova(lmPart,lmEmpty,test="Chi")
#take the value for the residual deviance and p-val ([1] is for null dev)
statDev[1] <- LRT$Deviance[2]
statChi[1] <- LRT$`Pr(>Chi)`[2]

nag <- nagelkerke(lmPart)
nagPart[1] <- nag$Pseudo.R.squared.for.model.vs.null[3]


#only perks
current <- perkFeatures
string <- "success ~"
for (j in 1:length(current)) {
  if(j==1){
    string <- paste(string,current[j])
  }else{
    string <- paste(string,"+",current[j])
  }
}
lmPart  <- glm(string, family = binomial(), data = data)
partBIC <- AIC(lmPart, k=log(nrow(data)))
partAIC <- AIC(lmPart, k=2)
bic[2] <- emptyBIC - partBIC
aic[2] <- emptyAIC - partAIC

#create log ratio test
LRT <- anova(lmPart,lmEmpty,test="Chi")
#take the value for the residual deviance and p-val ([1] is for null dev)
statDev[2] <- LRT$Deviance[2]
statChi[2] <- LRT$`Pr(>Chi)`[2]

nag <- nagelkerke(lmPart)
nagPart[2] <- nag$Pseudo.R.squared.for.model.vs.null[3]


#####################only project
current <- projectFeatures
string <- "success ~"
for (j in 1:length(current)) {
  if(j==1){
    string <- paste(string,current[j])
  }else{
    string <- paste(string,"+",current[j])
  }
}
lmPart  <- glm(string, family = binomial(), data = data)
partBIC <- AIC(lmPart, k=log(nrow(data)))
partAIC <- AIC(lmPart, k=2)
bic[3] <- emptyBIC - partBIC
aic[3] <- emptyAIC - partAIC

#create log ratio test
LRT <- anova(lmPart,lmEmpty,test="Chi")
#take the value for the residual deviance and p-val ([1] is for null dev)
statDev[3] <- LRT$Deviance[2]
statChi[3] <- LRT$`Pr(>Chi)`[2]

nag <- nagelkerke(lmPart)
nagPart[3] <- nag$Pseudo.R.squared.for.model.vs.null[3]


#calculate the explanation when the set is solo
print(nagPart/nagFull)

#create table for plot
lables <- c("entrepreneur","finance", "pitch")

res <- as.data.frame(cbind(lables,bic,statDev,statChi,pvalColor=(statChi<0.05)))
res$bic <- as.numeric(as.character(res$bic))
res$statDev <- as.numeric(as.character(res$statDev))
res$statChi <- round(as.numeric(as.character(res$statChi)),3)

#BIC plot
ggplot(res)+geom_bar(aes(x=reorder(lables, -bic), y=bic,fill="blue"), stat = "identity")+xlab("Added Feature (to intercept)")+ylab("BIC Difference (empty-part)")+ggtitle("First Step Forward (BIC)")+ theme(text = element_text(size=20))+scale_fill_manual(values = c("#ec7014"))


#BIC pie chart
colors <- c('rgb(216,179,101)', 'rgb(245,245,245)', 'rgb(90,180,172)')

plot_ly(data, labels = ~lables, values = ~bic, type = 'pie',
        textposition = 'inside',
        textinfo = 'label+percent',
        insidetextfont = list(color = '#000000'),
        hoverinfo = 'text',
        text = ~paste('$', bic, ' billions'),
        marker = list(colors = colors,
                      line = list(color = '#FFFFFF', width = 1)),
        #The 'pull' attribute can also be used to create space between the sectors
        showlegend = FALSE) %>%
  layout(title = 'BIC Difference % (From Total Difference) in Feature Sets',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         font=list(
           family = "Arial",
           size = 20,
           color = 'Black'))


#AIC plot
res3 <- as.data.frame(cbind(lables,aic))
res3$aic <- as.numeric(as.character(res3$aic))
ggplot(res3)+geom_bar(aes(x=reorder(lables, -aic), y=aic,fill="blue"), stat = "identity")+xlab("Added Feature (to intercept)")+ylab("AIC Difference (empty-part)")+ggtitle("Step Forward (AIC)")+ theme(text = element_text(size=20))+scale_fill_manual(values = c("#ec7014"))


# colors <- c('rgb(216,179,101)', 'rgb(158,154,200)', 'rgb(90,180,172)')
# colors <- c('rgb(158,154,200)', 'rgb(216,179,101)', 'rgb(90,180,172)')
colors <- c('rgb(156,190,189)', 'rgb(210,203,108)', 'rgb(217,217,217)')


#AIC pie chart
plot_ly(data, labels = ~lables, values = ~aic, type = 'pie',
        textposition = 'inside',
        textinfo = 'label+percent',
        insidetextfont = list(color = '#000000'),
        hoverinfo = 'text',
        text = ~paste('$', aic, ' billions'),
        marker = list(colors = colors,
                      line = list(color = '#FFFFFF', width = 1)),
        #The 'pull' attribute can also be used to create space between the sectors
        showlegend = FALSE) %>%
  layout(title = 'AIC Difference % (From Total Difference) in Feature Sets',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         font=list(
           family = "Arial",
           size = 20,
           color = 'Black'))



#deviance pie chart
statDev <- statDev*(-1)

plot_ly(data, labels = ~lables, values = ~statDev, type = 'pie',
        textposition = 'inside',
        textinfo = 'label+percent',
        insidetextfont = list(color = '#000000'),
        hoverinfo = 'text',
        text = ~paste('$', aic, ' billions'),
        marker = list(colors = colors,
                      line = list(color = '#FFFFFF', width = 1)),
        #The 'pull' attribute can also be used to create space between the sectors
        showlegend = FALSE) %>%
  layout(title = 'Deviance Difference % (From Total Difference) in Feature Sets',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         font=list(
           family = "Arial",
           size = 20,
           color = 'Black'))

rm(bic,res,res3,emptyBIC,lmEmpty,features,current,string,j,lmPart,partBIC, aic, emptyAIC, lables, partAIC,colors, perkFeatures, projectFeatures, userFeatures,LRT,statChi,statDev,nag,nagFull,nagPart)

```


#Correlation

Create correlation plot using spearman correlation for monotonicity.
This is in order to show sets have little correlation between them.

```{r}

corDat <- data[,1:(ncol(data))]
res <- round(cor(corDat,method = c("spearman")),2)


ggcorrplot(res,
           outline.col = "white",
           ggtheme = ggplot2::theme_gray,
           colors = c("#6D9EC1", "white", "#E46726"),insig = "blank",lab = TRUE)


```

