---
title: "Sections Analysis"
author: "Ofir Mizrahi"
date: "2018 M05 31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(corrplot)
library(ggcorrplot)
library(sqldf)
library(plotly)
```


#####################################################
understanding the top features by bic and aic
#####################################################

##Load Tables

We will load the 3 tables (mostly for thier feature names). We will use the rows from perk table as we only took away the INF values, we still want to predict success for users where this is not thier first project.
For each table, We took down features that in the feature analysis donated nothing.
```{r}
#project table
path <- "C:\\Users\\Ofir\\Desktop\\Thesis\\Kickstarter\\projectBinaryWeb.csv"
project <- read.csv(path, header = T)
project$X <- NULL

project <- project[,c(4:10,17)]
rm(path)

#user table
path <- "C:\\Users\\Ofir\\Desktop\\Thesis\\Kickstarter\\userBinaryWeb.csv"
user <- read.csv(path, header = T)
user$X <- NULL
user$continent <- NULL
user$noFacebookFriends <- NULL

rm(path)

#perk table
path <- "C:\\Users\\Ofir\\Desktop\\Thesis\\Kickstarter\\sandboxCleaned.csv"
temp <- read.csv(path, header = T)
temp$X <- NULL

perk <- temp[,c(6,27,29,31,44,50,55,25)]
perk <- perk[!c(perk$averageBackersRequired==Inf),]
rm(path,temp)


#create total table
path <- "C:\\Users\\Ofir\\Desktop\\Thesis\\Kickstarter\\sandboxCleaned.csv"
data <- read.csv(path, header = T)
data$X <- NULL
data <- data[!c(data$averageBackersRequired==Inf),]

#add personal attribute to total table
path <- "C:\\Users\\Ofir\\Desktop\\Thesis\\Kickstarter\\personalSite.csv"
temp <- read.csv(path, header = T)
temp$X <- NULL


data <- sqldf("select *
from data left join temp on temp.url=data.url")

data$url <- NULL
data$url <- NULL

#remove success to the end of table
temp <- data$success
data$success <- NULL
data$success <- temp

#select only relevant feature
features <- c(names(perk)[1:ncol(perk)-1],names(project)[1:ncol(project)-1],names(user)[1:ncol(user)])
userFeatures <- names(user)[1:ncol(user)-1]
perkFeatures <- names(perk)[1:ncol(perk)-1]
projectFeatures <- names(project)[1:ncol(project)-1]

data[is.na(data$personal),"personal"] <- 0
#screen data for only first projects or not
#data <- data[(data$created!=1),]
data <- data[,c(features)]


rm(user,perk,project, path, temp)
```


#Step Backward (BIC & AIC)

Create the steps excluding the entire set each time.
Because we don't want to penalize for number of features we use AIC as well but we can see results are the same.

```{r}
string <- "success ~"
for (j in 1:length(features)) {
  if(j==1){
    string <- paste(string,features[j])
  }else{
    string <- paste(string,"+",features[j])
  }
}

lmFull  <- glm(formula= string , family = binomial(), data = data)

#bic
fullBIC <- AIC(lmFull, k=log(nrow(data)))
fullAIC <- AIC(lmFull, k=2)

bic <- vector()
aic <- vector()

#No perks
current <- c(userFeatures,projectFeatures)
string <- "success ~"
for (j in 1:length(current)) {
  if(j==1){
    string <- paste(string,current[j])
  }else{
    string <- paste(string,"+",current[j])
  }
}
lmPart  <- glm(string, family = binomial(), data = data)
partBIC <- AIC(lmPart, k=log(nrow(data)))
partAIC <- AIC(lmPart, k=2)
bic[1] <- partBIC- fullBIC
aic[1] <- partAIC- fullAIC

#No user
current <- c(perkFeatures,projectFeatures)
string <- "success ~"
for (j in 1:length(current)) {
  if(j==1){
    string <- paste(string,current[j])
  }else{
    string <- paste(string,"+",current[j])
  }
}
lmPart  <- glm(string, family = binomial(), data = data)
partBIC <- AIC(lmPart, k=log(nrow(data)))
partAIC <- AIC(lmPart, k=2)
bic[2] <- partBIC- fullBIC
aic[2] <- partAIC- fullAIC


#No project
current <- c(userFeatures,perkFeatures)
string <- "success ~"
for (j in 1:length(current)) {
  if(j==1){
    string <- paste(string,current[j])
  }else{
    string <- paste(string,"+",current[j])
  }
}
lmPart  <- glm(string, family = binomial(), data = data)
partBIC <- AIC(lmPart, k=log(nrow(data)))
partAIC <- AIC(lmPart, k=2)
bic[3] <- partBIC- fullBIC
aic[3] <- partAIC- fullAIC


lables <- c("finance","entrepreneur", "pitch")

#BIC plot
res <- as.data.frame(cbind(lables,bic))
res$bic <- as.numeric(as.character(res$bic))
ggplot(res)+geom_bar(aes(x=reorder(lables, -bic), y=bic, fill="blue"), stat = "identity")+xlab("Excluded Feature (from full model)")+ylab("BIC Difference (part-full)")+ggtitle("Step Backwards (BIC)")+ theme(axis.text.x = element_text(angle = 45, hjust = 1))+scale_fill_manual(values = c("#3690c0"))

#AIC plot
res2 <- as.data.frame(cbind(lables,aic))
res2$aic <- as.numeric(as.character(res2$aic))
ggplot(res2)+geom_bar(aes(x=reorder(lables, -aic), y=aic, fill="blue"), stat = "identity")+xlab("Excluded Features (from full model)")+ylab("AIC Difference (part-full)")+ggtitle("Step Backwards (AIC)")+ theme(text = element_text(size=20))+scale_fill_manual(values = c("#3690c0"))

rm(bic,res,res2,fullBIC,lmFull,features,current,string,i,j,lmPart,partBIC, aic, fullAIC, lables, partAIC)
```

#Step Forward (BIC & AIC)

Create the steps including the entire set each time.
Because we don't want to penalize for number of features we use AIC as well but we can see results are the same.
Create pie charts as well to emphasize the difference between sets.

```{r}
lmEmpty <- glm(success ~ 1, family = binomial(), data = data)
emptyBIC <- AIC(lmEmpty, k=log(nrow(data)))
emptyAIC <- AIC(lmEmpty, k=2)


features <- names(data)[1:ncol(data)-1]
bic <- vector()
aic <- vector()

#only user
current <- userFeatures
string <- "success ~"
for (j in 1:length(current)) {
  if(j==1){
    string <- paste(string,current[j])
  }else{
    string <- paste(string,"+",current[j])
  }
}
lmPart  <- glm(string, family = binomial(), data = data)
partBIC <- AIC(lmPart, k=log(nrow(data)))
partAIC <- AIC(lmPart, k=2)
bic[1] <- emptyBIC - partBIC
aic[1] <- emptyAIC - partAIC


#only perks
current <- perkFeatures
string <- "success ~"
for (j in 1:length(current)) {
  if(j==1){
    string <- paste(string,current[j])
  }else{
    string <- paste(string,"+",current[j])
  }
}
lmPart  <- glm(string, family = binomial(), data = data)
partBIC <- AIC(lmPart, k=log(nrow(data)))
partAIC <- AIC(lmPart, k=2)
bic[2] <- emptyBIC - partBIC
aic[2] <- emptyAIC - partAIC

#only project
current <- projectFeatures
string <- "success ~"
for (j in 1:length(current)) {
  if(j==1){
    string <- paste(string,current[j])
  }else{
    string <- paste(string,"+",current[j])
  }
}
lmPart  <- glm(string, family = binomial(), data = data)
partBIC <- AIC(lmPart, k=log(nrow(data)))
partAIC <- AIC(lmPart, k=2)
bic[3] <- emptyBIC - partBIC
aic[3] <- emptyAIC - partAIC


lables <- c("entrepreneur","finance", "pitch")

res <- as.data.frame(cbind(lables,bic))
res$bic <- as.numeric(as.character(res$bic))
ggplot(res)+geom_bar(aes(x=reorder(lables, -bic), y=bic,fill="blue"), stat = "identity")+xlab("Added Feature (to intercept)")+ylab("BIC Difference (empty-part)")+ggtitle("Step Forward (BIC)")+ theme(text = element_text(size=20))+scale_fill_manual(values = c("#ec7014"))


res2 <- as.data.frame(cbind(lables,bic))
colors <- c('rgb(216,179,101)', 'rgb(245,245,245)', 'rgb(90,180,172)')

plot_ly(data, labels = ~lables, values = ~bic, type = 'pie',
        textposition = 'inside',
        textinfo = 'label+percent',
        insidetextfont = list(color = '#000000'),
        hoverinfo = 'text',
        text = ~paste('$', bic, ' billions'),
        marker = list(colors = colors,
                      line = list(color = '#FFFFFF', width = 1)),
                      #The 'pull' attribute can also be used to create space between the sectors
        showlegend = FALSE) %>%
  layout(title = 'BIC Difference % (From Total Difference) in Feature Sets',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         font=list(
  family = "Arial",
  size = 20,
  color = 'Black'))



res3 <- as.data.frame(cbind(lables,aic))
res3$aic <- as.numeric(as.character(res3$aic))
ggplot(res3)+geom_bar(aes(x=reorder(lables, -aic), y=aic,fill="blue"), stat = "identity")+xlab("Added Feature (to intercept)")+ylab("AIC Difference (empty-part)")+ggtitle("Step Forward (AIC)")+ theme(text = element_text(size=20))+scale_fill_manual(values = c("#ec7014"))


res4 <- as.data.frame(cbind(lables,aic))
colors <- c('rgb(216,179,101)', 'rgb(158,154,200)', 'rgb(90,180,172)')
colors <- c('rgb(158,154,200)', 'rgb(216,179,101)', 'rgb(90,180,172)')
colors <- c('rgb(156,190,189)', 'rgb(210,203,108)', 'rgb(217,217,217)')



plot_ly(data, labels = ~lables, values = ~aic, type = 'pie',
        textposition = 'inside',
        textinfo = 'label+percent',
        insidetextfont = list(color = '#000000'),
        hoverinfo = 'text',
        text = ~paste('$', aic, ' billions'),
        marker = list(colors = colors,
                      line = list(color = '#FFFFFF', width = 1)),
                      #The 'pull' attribute can also be used to create space between the sectors
        showlegend = FALSE) %>%
  layout(title = 'AIC Difference % (From Total Difference) in Feature Sets',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         font=list(
  family = "Arial",
  size = 20,
  color = 'Black'))

rm(bic,res,res2,res3,res4,emptyBIC,lmEmpty,features,current,string,j,lmPart,partBIC, aic, emptyAIC, lables, partAIC,colors, perkFeatures, projectFeatures, userFeatures)

```


#Correlation

Create correlation plot using spearman correlation for monotonicity.
This is in order to show sets have little correlation between them.

```{r}

corDat <- data[,1:(ncol(data))]
res <- round(cor(corDat,method = c("spearman")),2)


ggcorrplot(res,
   outline.col = "white",
   ggtheme = ggplot2::theme_gray,
   colors = c("#6D9EC1", "white", "#E46726"),insig = "blank",lab = TRUE)


```

